Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-04 papers/B1555_EdgeOn/B1555_letter.tex
change text in Discussion

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk components. Our models predict the radio image positions and also flux ratio anomalies, which the 1-SIE model in \citet{Marlow} fails. Since radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}, our successful modelling indicates that the structure from lens galaxy itself can cause radio flux ratio anomalies. An edge-on disk with high ellipcity in lens models well explains the observed flux ratios without the presense of substructrues. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasars indicate the existence of substructures. A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in the system. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. One must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. For precise estimation on substurcture population, mass function, or any derived properties from strong lensed flux anomalous quasars, non-substructure effects are important to be understood beforehand.

Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars. While radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With an high ellipcity edge-on disk, our new lens models well explain the flux ratio anomalies. Lack of knowledge on lens galaxy can lead to an improper lens model and thus cause bias to statics and derived properties among substructure detection. With the first system being analyzed and shown that an edge-on disk from lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\

>>>>

In part 3, we present new lens models of B1555+375. The most significant difference comparing to previous modelling is a new edge-on disk component. With a bulge plus an edge-on disk, our models fairly match the radio image positions and also flux ratio anomalies, while models with only one SIE component \citep{Marlow,Xu14} fail. Radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}. Our successful modelling indicates that the structure from lens galaxy itself causes the flux ratio anomalies in B1555+375. An edge-on disk with high ellipcity well explains the observed flux ratios without the presense of substructrues. This breaks the idea that in strongly lensed quasars, radio flux ratio anomalies are most likely originated from substructure perturbations. It is worth noticing not all of flux ratio anomalies in lensed quasars indicate the existence of substructures. Our discover shows a complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in the system. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. To gather correct statistics, one must fully consider non-substructure effects. Otherwise, possible ``false'' substructures detected by flux anomalies can serverly biased the data analysis. Even with real substructures presence, lens galaxy structure can still dominate the flux anomalous phenomenon and have impact on estimated mass and also other derived properties. We would like to draw attention on this non-substructure effect brought by a large, high ellipcity edge-on disk. For precise measurement on substurcture population, mass function, and any derived properties from strong lensed flux anomalous systems, careful estimation on non-substructure effects are important.

Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars. Although radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With an high ellipcity edge-on disk, our new lens models well explain the flux ratio anomalies. Lack of knowledge on lens galaxy can lead to an improper lens model and thus cause bias to statics and derived properties among substructure detection. With the first system being analyzed and shown that an edge-on disk from lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
